\bf On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2024-11-25 Manuscript/reply.tex
smoothed discussion
removed resolved, fixed minor typos

The manuscript has been revised accordingly with the following most
notable changes:
\begin{enumerate}
\item
  The focus of the study has been clarified in the completely
  rewritten introduction. The two objectives are 1) to investigate
  whether the reaction times at the 2022 World Championships were
  significantly different from the other competitions; and 2) to
  assess the appropriateness of the 0.1-second threshold.
\item
  Additional data (reaction times from the 100-meter dash) have been
  added to the analysis for both objectives to expand the scope of the
  analysis and derive better insights.
\item
  In the assessment of the 0.1-second threshold, the Gamma GLMM has
  been replaced with a generalized Gamma distributions in the flexible
  framework of Generalized Additive Models for Location, Scale, and
  Shape (GAMLSS) \citep{stasinopoulos2024generalized}, with random
  effects of venue and heat in two of its parameters, respectively.
  The new model provides an adequate fit to the data, as confirmed by
  diagnostic checks.
\end{enumerate}

@@

In the revision, we have added explanation about why 100-meter dash
data for both men and wemen were included, while 200-meter dash data
were not included in our analysis in the opening paragraph of Section~2.
The subsequent analyses in the manuscript have been updated with the
expanded datasets.
\eds{let's revisit this again after objective 2 analyses are set}

@@

Thank you for this thoughtful suggestion. We apologize for any
confusion regarding the heat effect. In our model, the heat effect
captures the speed-level of the heat rather than the type of heat
(e.g., preliminary vs. final). To clarify this, we have added
additional explanations in the first paragraph of Section~3.2 to
explicitly define the venue and heat effects. We avoided calling it a
``race effect'' to prevent misinterpretation as referring to the
athlete's race.

@@

In the revision, we replaced the Gamma GLMM with a generalized Gamma
distribution in the GAMLSS framework. The venue effect and heat effect
were incorporated into two parameters controlling the scale of the
distribution. This revised model provides an improved and adequate fit
to the data compared to the original Gamma GLMM.
\eds{let's revisit this again after objective 2 analyses are set}

@@

Thank you for the positive feedback. We have expanded both the rank
comparison and the GAMLSS model sections with additional data to
strengthen our analysis. These enhancements support our findings of an
anomaly in 2022 and highlight that the 0.1-second reaction time
threshold lacks a foundation in formal statistical evidence.
\eds{let's revisit this again after objective 2 analyses are set}

@@

For the approximately 20 disqualified athletes with positive reaction
times, we examined the impact of including them in the analysis. The
probability of observing a reaction time below 0.1 seconds increased
\jy{Are these based on the expanded dataset or the original dataset?}
\jy{These numbers need to be updated}
slightly from 0.0029 to 0.0039, with similar parameter estimates for
the random effects. Given these results, we opted to include these
observations in the dataset.

@@

Thank you for this suggestion. Unfortunately, comprehensive data on 
Devon Allen’s reaction times is not readily available. While we gathered 
as much data as possible from publicly available sources, reaction times 
are typically recorded only at major competitions, such as national and 
world championships. As a result, the dataset is too limited to support 
a formal statistical analysis of his reaction times.
To address this point, we have added a brief discussion in 
paragraph~??? of the Discussion Section, noting the limitations in data 
availability and the implications of this issue.

@@

Thank you for pointing out the need for clearer intrepretation of
Table~2.
\jy{Owen: please add standard errors of the three intercept  to the table.}
The table now contains fitted parameters of the generalized Gamma
distribution GAMLSS as specified Equations (1)--(3). The table caption has been
expanded to provide detailed explanations of the fitted parameters.

>>>>

The manuscript has been revised accordingly with the following most
notable changes:
\begin{enumerate}
\item
  The focus of the study has been clarified in the completely
  rewritten introduction. The two objectives are 1) to investigate
  whether the reaction times at the 2022 World Championships were
  significantly different from the other competitions; and 2) to
  assess the appropriateness of the 0.1-second threshold.
\item
  Additional data (reaction times from the 100-meter dash) have been
  added to the analysis for both objectives to expand the scope of the
  analysis and derive better insights.
\item
  In the assessment of the 0.1-second threshold, the Gamma GLMM has
  been replaced with a generalized Gamma distributions in the flexible
  framework of Generalized Additive Models for Location, Scale, and
  Shape (GAMLSS) \citep{stasinopoulos2024generalized}, with random
  effects of venue and heat in two of its parameters, respectively.
  The new model provides an adequate fit to the data, as confirmed by
  diagnostic checks.
\item
  Given the expanded dataset and change to GAMLSS, the corresponding
  sections of the paper, including data preparation, methods, results,
  and discussions have all been rewritten at large.
\end{enumerate}

@@

In the revision, we have added explanation about why 100-meter dash
data for both men and wemen were included, while 200-meter dash data
were not included in our analysis in the opening paragraph of Section~2.
The subsequent analyses in the manuscript have been updated with the
expanded datasets.

@@

Thank you for this thoughtful suggestion. We apologize for any
confusion regarding the heat effect. In our model, the heat effect
captures the speed-level of the heat rather than the type of heat
(e.g., preliminary vs. final). To clarify this, we have added
additional explanations Section~3.2 (after Equation (3)) to
explicitly define the venue and heat effects. We avoided calling it a
``race effect'' to prevent misinterpretation as referring to the
athlete's race.

@@

In the revision, we replaced the Gamma GLMM with a generalized Gamma
distribution in the GAMLSS framework. The venue effect and heat effect
were incorporated into two parameters controlling the scale of the
distribution. This revised model provides an improved and adequate fit
to the data compared to the original Gamma GLMM.

@@

Thank you for the positive feedback. We have expanded both the rank
comparison and the GAMLSS model sections with additional data to
strengthen our analysis. These enhancements support our findings of an
anomaly in 2022 and highlight that the 0.1-second reaction time
threshold lacks a foundation in formal statistical evidence.

@@

For the approximately 20 disqualified athletes with positive reaction
times, we examined the impact of including them in the analysis. The
probability of observing a reaction time below 0.1 seconds increased
\jy{Are these based on the expanded dataset or the original dataset?}
\jy{These numbers need to be updated}
slightly from 0.0029 to 0.0039, with similar parameter estimates for
the random effects. Given these results, we opted to include these
observations in the dataset.
\eds{Currently the text in the manuscript suggests we are including a 
sensitivity analysis in the Supplement for the analysis without the positive DQs.
If we are indeed including that, we should mention that here too. (If not, we 
need to remove that statement from the main manuscript.)}

@@

Thank you for this suggestion. Unfortunately, comprehensive data on 
Devon Allen’s reaction times is not readily available. While we gathered 
as much data as possible from publicly available sources, reaction times 
are typically recorded only at major competitions, such as national and 
world championships. As a result, the dataset is too limited to support 
a formal statistical analysis of his reaction times.
To address this point, we have added a brief discussion in the first 
paragraph of the Discussion Section, noting the limitations in data 
availability and the implications of this issue.

@@

Thank you for pointing out the need for clearer interpretation of
Table~2.
\jy{Owen: please add standard errors of the three intercept  to the table.}
The table now contains fitted parameters of the generalized Gamma
distribution GAMLSS as specified Equations (1)--(3). The table caption has been
expanded to provide detailed explanations of the fitted parameters.
